Hierarchical System Builder Toolset

### 2025-01-10 v2/HierSysBuild/docs/tutorial/HierSysTools.tex
Updated Hier Sys Builder to allow the use of internally generated clocks (good luck!)

A 4-stage shift register constructed out of two simpler
2-stage shift registers.
\begin{verbatim}
$system shift_reg_4 $library shiftreg_library
   $in 
       $pipe in_data 32 $depth 2
   $out 
       $pipe out_data 32 $depth 2
{
   // internal pipe description..
   $pipe mid_data 32 depth 2
   $instance sr_left shiftreg_library :  shift_reg_2
                in_data => in_data
                out_data => mid_data
   $instance sr_right shiftreg_library :  shift_reg_2
                in_data => mid_data
                out_data => out_data
}
\end{verbatim}
}

@@

\frame[containsverbatim]{\frametitle{Using RTL State Machine: example shift\_reg\_4\_rtl}
\begin{itemize}
\item Essentially the same as shift\_reg\_4 example, but without aa2c simulation setup.
\item Examine the build and make files to see the differences.
\item Note: only VHDL sim verificationis supported for now.
\end{itemize}
}

>>>>

A 4-stage shift register is constructed out of two simpler
2-stage shift registers.
\begin{verbatim}
$system shift_reg_4 $library shiftreg_library
   $in 
       $pipe in_data 32 $depth 2
   $out 
       $pipe out_data 32 $depth 2
{
   // internal pipe description..
   $pipe mid_data 32 depth 2
   $instance sr_left shiftreg_library :  shift_reg_2
                in_data => in_data
                out_data => mid_data
   $instance sr_right shiftreg_library :  shift_reg_2
                in_data => mid_data
                out_data => out_data
}
\end{verbatim}
}

@@

\frame[containsverbatim]{\frametitle{Using RTL State Machines: example shift\_reg\_4\_rtl}
\begin{itemize}
\item Essentially the same as shift\_reg\_4 example, but without aa2c simulation setup.
\item Examine the build and make files to see the differences.
\item Note: only VHDL sim verificationis supported for now.
\end{itemize}
}

\frame[containsverbatim]{\frametitle{Clocks and resets}
\begin{itemize}
\item By default, each block in the system operates on 
clock {\em clk} and reset {\em reset}.  The reset is
active high and synchronized to {\em clk}.
\item It is possible to define alternative clock and
reset signals used in a system.
\item It is possible to map one of these alternative clocks
and resets to the default clock/reset on a subsystem instance.
\end{itemize}
}

\frame[containsverbatim]{\frametitle{Declaring clock-like and reset-like signals}
\begin{verbatim}
$system Top $library TopLib
   $in
     $pipe A
     $signal $clk EXTCLK 1 $depth 1
     $signal $reset EXTRESET 1 $depth 1
   $out
     $pipe B
{
}
\end{verbatim}
Here, we are stating that the input signal EXTCLK is clock-like
and the input signal RESET is reset-like.
}

\frame[containsverbatim]{\frametitle{Using clock-like and reset-like signals}
\begin{verbatim}
// ... as above ... 
{
 $pipe TMP $clk => EXTCLK $reset =>  EXTRESET
 $instance i0  S1:Stage1
         ..
         $clk => EXTCLK
         $reset => EXTRESET

 $instance i1  S2:Stage2
         ...
         $clk => EXTCLK
         $reset => EXTRESET

\frame[containsverbatim]{\frametitle{Using clock-like and reset-like signals}
\begin{itemize}
\item We have declared EXTCLK as clock-like and EXTRESET as reset-like.
\item Pipe TMP and instance i0 will operate with EXTCLK connected
to their default clock input and EXTRESET connected to their default
reset input.
\item We have generated a local clock EXTCLK\_REPEATED using an
RTL machine.
\item Instance i0 will operate with EXTCLK\_REPEATED connected
to its default clock input and EXTRESET connected to its default
reset input.
\item Only a clock-like signal can be mapped to the default clock.
\item Only a reset-like signal can be mapped to the default reset.
\end{itemize}
}

\frame[containsverbatim]{\frametitle{Example: using clock-like and reset-like signals}
See the example clocks\_and\_resets.
